Details of specific functions

### 2019-08-12 inst/gitbook/03_specific-tutorials.Rmd
added plot preview function

>>>>

Note that all the options above are plotting disparity objects for which a disparity metric *has been calculated*.
This makes totally sense for `dispRity` objects but sometimes it might be interesting to look at what the trait-space looks like before measuring the disparity.
This can be done by plotting `dispRity` objects with no calculated disparity!

For example, we might be interested in looking at how the distribution of elements change as a function of the distributions of different sub-settings.
For example custom subsets *vs.* time subsets:

```{r, fig.width=8, fig.height=4}
## Making the different subsets
cust_subsets <- custom.subsets(BeckLee_mat99, crown.stem(BeckLee_tree, inc.nodes = TRUE))
time_subsets <- chrono.subsets(BeckLee_mat99, tree = BeckLee_tree, method = "discrete", time = 5)

## Note that no disarity has been calculated here:
is.null(cust_subsets$disparity)
is.null(time_subsets$disparity)

## But we can still plot both spaces by using the default plot functions
par(mfrow = c(1,2))
## Default plotting
plot(cust_subsets)
## Plotting with more arguments
plot(time_subsets, dimensions = c(4,5), main = "Some \"low\" dimensions")
```

> DISCLAIMER: This functionality can be handy for exploring the data (e.g. to visually check whether the subset attribution worked) but it might be misleading on how the data is *actually* distributed in the multidimensional space!
Groups that don't overlap on two set dimensions can totally overlap in all other dimensions!
